### 2015-03-12 cv-body.tex
Update CV - yay Smith!
Fix typo in CV
Update CV
Candidate -> PhD

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2011--14]
Ph.D.\ Candidate, Simon Fraser University, Burnaby, Canada\\ Supervisors:
Dr.\ Nicholas K. Dulvy and Dr.\ Andrew B. Cooper\\ Canadian Fulbright
Scholar to the University of Washington in 2012--13
\item[2008--10]
M.Sc.\ Biology, Dalhousie University, Halifax, Canada\\ Thesis title:
Trends, drivers, and ecosystem effects of expanding global invertebrate
fisheries. Supervisor: Dr.\ Heike K. Lotze.
(\href{http://seananderson.ca/papers/Anderson_MSc_2010.pdf}{PDF})\\
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2004--07]
B.Sc.\ (Hons.) Environmental Science, Dalhousie University, Halifax,
Canada\\ Thesis title: How sustainable are emerging low-trophic level
fisheries on the Scotian Shelf? Supervisors: Dr.\ Heike K. Lotze and
Dr.\ Ransom A. Myers.
(\href{http://seananderson.ca/papers/Anderson_HSc_2006.pdf}{PDF})\\
First Class Honours \& Environmental Programmes Honour Society Medal
\item[2001--03]
B.Sc.\ Candidate (Hons.) Kinesiology, University of Waterloo, Waterloo,
Canada Transferred to Dalhousie University in 2004.
\end{description}

@@

@@

Monahan, M.L. Muradian, K. Ono, K.A. Vert-Pre, A.R. Whitten, A.E. Punt.

@@

Ecological Applications. In press.

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Orzechowski, E.A., R. Lockwood, J.E. Byrnes, \textbf{S.C. Anderson}, S.
Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
Lotze, C.R. McClain, J.L. McGuire, A. O'Dea, J.M. Pandolfi, C. Simpson,
D.P. Tittensor. Determinants of extinction selectivity over the last 500
million years: a meta-analysis of marine bivalves and gastropods.
Submitted.
\item[2015]
Finnegan*, S., \textbf{S.C. Anderson}*, P.G. Harnik*, C. Simpson, D.P.
Tittensor, J.E. Byrnes, Z.V. Finkel, D.R. Lindberg, L.H. Liow, R.
Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.
Pandolfi. Paleontological baselines for evaluating extinction risk in
the modern oceans. In review. (*Authors contributed equally).
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2014]
Garfield Weston Foundation / BC Packers Ltd. Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington in
2012--13
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

>>>>

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2011--15]
Ph.D.\ Biology, Simon Fraser University, Burnaby, Canada\\ Supervisors:
Dr.\ Nicholas K. Dulvy and Dr.\ Andrew B. Cooper\\ Canadian Fulbright
Scholar to the University of Washington in 2012--13
\item[2008--10]
M.Sc.\ Biology, Dalhousie University, Halifax, Canada\\ Thesis title:
Trends, drivers, and ecosystem effects of expanding global invertebrate
fisheries. Supervisor: Dr.\ Heike K. Lotze.
(\href{http://seananderson.ca/papers/Anderson_MSc_2010.pdf}{PDF})\\
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2004--07]
B.Sc.\ (Hons.) Environmental Science, Dalhousie University, Halifax,
Canada\\ Thesis title: How sustainable are emerging low-trophic level
fisheries on the Scotian Shelf? Supervisors: Dr.\ Heike K. Lotze and
Dr.\ Ransom A. Myers.
(\href{http://seananderson.ca/papers/Anderson_HSc_2006.pdf}{PDF})\\
First Class Honours \& Environmental Programmes Honour Society Medal
\item[2001--03]
B.Sc.\ Candidate (Hons.) Kinesiology, University of Waterloo, Waterloo,
Canada Transferred to Dalhousie University in 2004.
\end{description}

@@

\item[2015]

@@

Monnahan, M.L. Muradian, K. Ono, K.A. Vert-Pre, A.R. Whitten, A.E. Punt.

@@

Ecological Applications. 2015. 25(2): 559--572.

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Orzechowski, E.A., R. Lockwood, J.E. Byrnes, \textbf{S.C. Anderson}, S.
Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
Lotze, C.R. McClain, J.L. McGuire, A. O'Dea, J.M. Pandolfi, C. Simpson,
D.P. Tittensor. Determinants of extinction selectivity over the last 500
million years: a meta-analysis of marine bivalves and gastropods. In
revision.
\item[2015]
Finnegan*, S., \textbf{S.C. Anderson}*, P.G. Harnik*, C. Simpson, D.P.
Tittensor, J.E. Byrnes, Z.V. Finkel, D.R. Lindberg, L.H. Liow, R.
Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.
Pandolfi. Paleontological baselines for evaluating extinction risk in
the modern oceans. In review. (*Authors contributed equally).
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
David H. Smith Conservation Postdoctoal Research Fellowship
\item[2015]
Natural Sciences and Engineering Research Council of Canada Postdoctoral
Fellowship
\item[2014]
Garfield Weston Foundation / BC Packers Ltd. Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington in
2012--13
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}
